### 2023-01-17 Draft_GFC.tex
New_upload

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL 
\usepackage{tabularx}
%\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{0}

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{-.3in}%
\addtolength{\topmargin}{-.8in}%
\usepackage{amsmath,amssymb,amsthm,amsfonts,amstext,amsbsy,amscd,stmaryrd}
\usepackage{amssymb,amsmath,comment,subcaption,graphicx}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{cancel}
\usepackage{tikz}
\usepackage{subcaption} 
\usetikzlibrary{patterns}
\usepackage{xcolor}
\usepackage{bbm}
\usepackage{float}
\usepackage{color}
\usepackage{relsize}
\usepackage{diagbox}
\newcommand{\modif}[1]{{\begin{modification}#1\end{modification}}}
\newcommand{\ele}[1]{{\color{red}#1}}
%\UseRawInputEncoding
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{mathrsfs}
\newcommand{\rmd}{{\mathrm{d}}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Z}{\mathbb{Z}}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\E}{\operatorname{\mathbb{E}}}
\newcommand{\Var}{\operatorname{Var}}
\newcommand{\Cov}{\mathrm {Cov}}
\newcommand{\rme}{{\rm e}}
\renewcommand{\tilde}{\widetilde}
\renewcommand{\hat}{\widehat}
\newcommand{\TC}{\mathrm{TC}}
\newcommand{\TaC}{\mathrm{TaC}}
\newcommand{\LTC}{\mathrm{LTC}}
\newcommand{\LP}{\mathrm{LP}}
\newcommand{\Per}{\mathrm{Per}}
\theoremstyle{Theorem}
\newtheorem{Theorem}{Theorem}[section]
\newtheorem{Corollary}[Theorem]{Corollary}
\newtheorem{Lemma}[Theorem]{Lemma}
\newtheorem{Proposition}[Theorem]{Proposition}
\newtheorem{Definition}[Theorem]{Definition}
\theoremstyle{definition}
\newtheorem{remark}{Remark}
\renewcommand{\labelitemi}{\textperiodcentered}
\allowdisplaybreaks
\usepackage{ifpdf}
\ifpdf
\else
\usepackage{graphicx}
\DeclareGraphicsExtensions{.eps,.jpg,.png}
\fi
\usepackage{epstopdf}
\usepackage{array}
\usepackage{enumitem}
\newcounter{Ax}
\newcommand{\itemA}{%
    \addtocounter{Ax}{1}
    \item[A\theAx.]}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}

@@

\tikzset{
  mycross/.pic={
    \draw[pic actions] 
      (-2pt,0) -- (2pt,0)
      (0,-2pt) -- (0,2pt);
  },
 \newcolumntype{C}[1]{>{\centering\arraybackslash$}p{#1}<{$}}
\begin{document}
\section{Introduction}

@@

By using standard ellipse, they can compute the direction of maximum variability in a direction of angle $\theta$. So, they are able to describe the spatial behavior of the mean vectors, quantifying by the calculation of $\theta$ the direction of maximum variability

@@

Let $m$ be an integer with $m \geq 2$. Without loss of generality, we consider our observation window as the unit square $S = [0,m]^{2}$ and  we divide our window into $m^{2}$ pairwise disjoint squares. We denote by $e_1$, $e_{2}$ the elements of the canonical base of $\mathbb{R}^{2}$ and 

@@

 \item[$\bullet$] $\mathbb{G}_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \, \mathbb{Z}^{2}$ the set of points in $S$, to ease up the notations we write $x = (x_1, x_2)$ with $x_1, x_2 \in \{0,\ldots, m-1\}$ for any $x\in \mathbb{G}_{m}$.
 \item[$\bullet$] For $x\in \mathbb{G}_{m}, \; C_{m}(x) \, := \,x + \text{\larger[1]{$[$}}0, 1 \text{\larger[1]{$]$}}^{2} \subset S$, the $C_{m}(x)$ will be referred to as \textit{cells}.
\item[$\bullet$] And finally, we denote by  $\mathbb{E}^{(1)}_{m}, \; \mathbb{E}^{(2)}_{m} $ the set of vertical and horizontal edges in $\mathring{S}$, for each $x \in \mathbb{G}_{m}$,  $i \in \{1, 2\}$, the edge $w_{i}(x)$ is a segment of length $1$ and belongs to~$C_{m}(x) \cap C_{m}(x+e_{i})$. The cardinality of the sets of edges

@@

$\left\{ x \in \mathbb{G}_{m}; w_{1}(x) \in \mathbb{E}^{\scriptscriptstyle  (1)}_{m}\right\} = \left\{x \in \llbracket 0, m-1 \rrbracket^{2}, w_{1}(x) \in C_{m}(x) \cap C_{m}(x+e_{1})\right\} $\\ 
 \hspace*{4.25cm}$ =  \left\{ 1, m - 1\right\}\times\left\{ 0, m-1 \right\},$
\item$\left\{ x \in \mathbb{G}_{m}; w_{2}(x) \in \mathbb{E}^{\scriptscriptstyle  (2)}_{m}\right\}  = \left\{x \in \llbracket 0, m-1 \rrbracket^{2}, w_{2}(x) \in C_{m}(x) \cap C_{m}(x+e_{2}) \right\} $\\ 
 \hspace*{4.25cm}$ = \left\{ 0, m-1 \right\} \times \left\{ 1, m - 1\right\},$

@@

\draw[pattern=north west lines, pattern color=blue] (0,0) rectangle (1,1);
\draw[pattern=north west lines, pattern color=blue] (3,1) rectangle (2,2);
\foreach \x in {0,1,2,3}{
  \foreach \y in {0,1,2,3}{
  \draw[fill = red] (\x,\y) circle (2pt);

@@

\caption{Tiling with squares for $m = 4$ and associated cells $C_{4}(0,0)$ and $C_{4}(2,1)$ (blue stripes) and red point of $\mathbb{G}_{m}$.}

@@

\vspace{-1.5cm}

@@

    {\includegraphics[scale=0.25]{GaussianUn.pdf}}
    {\includegraphics[scale=0.25]{GaussianZUn.pdf}}
    {\includegraphics[scale=0.25]{GaussianZZZUn.pdf}}

@@

 \caption{Generations of Gaussian random fields with covariance $\rho(x) = e^{-\kappa||x||^{2}}$ with $m = 1024$, and different values for $\kappa$, from left to right $\kappa = 0.01, 0.1, 1$, using the Matlab function \textit{stationary Gaussian process} \cite{MATLAB}.}

@@

Considering a threshold parameter $t \in \mathbb{R}$, we introduce the associated binary \linebreak image $Z^{\scriptscriptstyle (m)}_{t} = \left(\mathbbm{1}_{\left\{X_x \geq t\right\}} \right)_{x \in \mathbb{G}_{m}}$ where each cell $C_{m}(x)$ is associated to black or white according to whether~$X_{x} \geq t$ or $X_{x} \leq t$. 

@@

For $t\in \mathbb{R},$ we denote by $\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t)$ the sum of all contributions over the $i$th direction (vertical for $i = 1$ and horizontal for $i = 2$). Then, the oriented perimeter of the binary image $Z^{\scriptscriptstyle (m)}$ is given by

@@

This result extends the one given in \cite{HermineAgnes} (Proposition 3) since we do not assume here that $\rho(e_i) > 0$. 

@@

\paragraph{Total variation.}
\textcolor{red}{
In image processing, the total variation of an image $u \in L^{1}_{loc}(\Omega)$ which is given by $\int_{\Omega}|\nabla u|dx$ is a common and well studied object. It is possible to link this quantity the perimeter of $u$, by applying the coarea formula, $\int_{\Omega}|\nabla u|dx = \int_{\mathbb{R}}\mathcal{P}(t)dt$ with $\mathcal{P}(t)$ being the perimeter associated to the level set of the image $u$ at level $t$. In the following result, by considering Proposition \eqref{propFisrtmoment}, we obtain a simple expression for the first moment of the total variation, and link it directly to the covariance evaluated in the $i$th direction.}

@@

\textcolor{red}{Let us now study the monotonic properties of the function $\rho \mapsto \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}(t)\right)$ where $\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}$ is the perimeter with respect of the orientation $i$ associated to the Gaussian field of covariance function $\rho$. This result allows us to state that the oriented perimeter is a strictly decreasing function with respect to $\rho$. }

@@

\textcolor{red}{Let $\overline{X}, \tilde{X}$ be two stationary centered Gaussian random fields with unit variance, and $\bar{\rho}, \tilde{\rho}$ their respective covariance structure. For any level $t$, we  have the following result:}

@@

\textcolor{red}{TCL}

@@

where $\xrightarrow[]{d}$ holds for the convergence in distribution and $\mathcal{N}\left(0,\,\Sigma_{2r}^{\star}\right)$ for the $2r$-dimensional centered Gaussian distribution with covariance matrix $\Sigma^\star_{2r}$ given by

@@

\Sigma^{\star}_{2r}(l,i,k,j) & : = \lim_{m \to \infty}\text{Cov}\left(\frac{1}{m}\mathcal{P}^{\scriptscriptstyle (i)}_{m}(t_{l}),  \frac{1}{m}\mathcal{P}^{\scriptscriptstyle (j)}_{m}(t_{k}) \right)

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{url} 
\usepackage{tabularx}

\newcommand{\blind}{0}

\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{-.3in}%
\addtolength{\topmargin}{-.8in}%
\usepackage{amsmath,amssymb,amsthm,amsfonts,amstext,amsbsy,amscd,stmaryrd}
\usepackage{amssymb,amsmath,comment,subcaption,graphicx}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{cancel}
\usepackage{tikz}
\usepackage{subcaption} 
\usetikzlibrary{patterns}
\usepackage{xcolor}
\usepackage{bbm}
\usepackage{float}
\usepackage{color}
\usepackage{relsize}
\usepackage{diagbox}
\newcommand{\modif}[1]{{\begin{modification}#1\end{modification}}}
\newcommand{\ele}[1]{{\color{red}#1}}
%\UseRawInputEncoding
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{mathrsfs}
\newcommand{\rmd}{{\mathrm{d}}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Z}{\mathbb{Z}}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\E}{\operatorname{\mathbb{E}}}
\newcommand{\Var}{\operatorname{Var}}
\newcommand{\Cov}{\mathrm {Cov}}
\newcommand{\rme}{{\rm e}}
\renewcommand{\tilde}{\widetilde}
\renewcommand{\hat}{\widehat}
\newcommand{\TC}{\mathrm{TC}}
\newcommand{\TaC}{\mathrm{TaC}}
\newcommand{\LTC}{\mathrm{LTC}}
\newcommand{\LP}{\mathrm{LP}}
\newcommand{\Per}{\mathrm{Per}}
\theoremstyle{Theorem}
\newtheorem{Theorem}{Theorem}[section]
\newtheorem{Corollary}[Theorem]{Corollary}
\newtheorem{Lemma}[Theorem]{Lemma}
\newtheorem{Proposition}[Theorem]{Proposition}
\newtheorem{Definition}[Theorem]{Definition}
\theoremstyle{definition}
\newtheorem{remark}{Remark}
\renewcommand{\labelitemi}{\textperiodcentered}
\allowdisplaybreaks
\usepackage{ifpdf}
\ifpdf
\else
\usepackage{graphicx}
\DeclareGraphicsExtensions{.eps,.jpg,.png}
\fi
\usepackage{epstopdf}
\usepackage{array}
\usepackage{enumitem}
\newcounter{Ax}
\newcommand{\itemA}{%
    \addtocounter{Ax}{1}
    \item[\textbf{A}\theAx.]}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}

@@

\tikzset{
  mycross/.pic={
    \draw[pic actions] 
      (-2pt,0) -- (2pt,0)
      (0,-2pt) -- (0,2pt);
  },
}
 \newcolumntype{C}[1]{>{\centering\arraybackslash$}p{#1}<{$}}
\begin{document}
\section{Introduction}

The main objective of our study is to be able to decide whether the texture of a grey-level image is isotropic or not. By the texture of an image, we mean the microscopic structure that is captured by the covariance function at the pixels scale. In order to achieve this goal, we propose a methodology built on a statistical test for which all components are rigourously validated. The originality of our approach is to stick on the geometrical features of the image without trying to identify the full distribution of the pixels values. Let us first start with an exemple of medical images where our methodology is applied.

\begin{figure}[H]
\centering
{\includegraphics[scale=0.5]{imagesstationarisee.pdf}}
 \caption{Stationnarized image of a bone x-ray, with it's associted excursion sets thresholded at the first, second and third quartile.}
\label{fig22}
\end{figure}

Let $\alpha \in (0,1)$ and $t_{\alpha} = F^{-1}_{X}(\alpha)$ be the associated quantile of the image $X$. We consider the thresholded image at level $t_{\alpha}$, $\{X > t_{\alpha}\}$, and then 
%compute the horizontal and vertical perimeter of each thresholded image, thus obtaining for each level $t_{\alpha}$, $(P^{(1)}_{i}(t_{\alpha}))_{i \leq 245}$, 
count the respective numbers of horizontal and vertical edges that are involved in the perimeter of the black region of the binary image. In case of an isotropic texture, the ratio of these two counters should be close to one. At the opposite, if the observed ratio is far from one, then some anisotropy is expected in the microscopic texture of the image.

The ratio has been computed for each image of the panel at various quantile levels. In Figure \ref{fig2}, the distribution of the obtained ratios is summerized in a boxplot for each level.

\begin{figure}[H]
  \centering  
   {\includegraphics[scale=0.28]{BoxplotRDAu.pdf}}
    \hspace{0.2cm}
 \caption{For $\alpha \in [0.15, 0.9]$, we represent on the left, the confidence interval of the mean of the ratio between the two oriented perimeters computed for $t_{\alpha}, \mathcal{P}^{1}(t_{\alpha}), \mathcal{P}^{2}(t_{\alpha})$ and its corresponding boxplot for real thresholded images of bone X-rays.}
\label{fig2}
\end{figure}

We observe that the boxplots of the ratio between the horizontal and vertical counters are not distributed around one, whatever the observed level. 
Moreover, for almost all images the observed ratios are above one whereas for some images extreme values are observed below one. We checked the fact that these extreme cases below one all belong to the same small group of images. Apparently, these images were subject to a $\pi/2$-angle rotation. Nevertheless, what is relevant on this sample of X-ray images of calcaneus is that the anisotropy of the texture can be revealed at any threshold level by simply comparing two single counters. It is worth to note that this anisotropy, although obvious through the proposed image analysis procedure, is not perceptible to the naked eye.

With a very different approach based on quadratic variations, the same sample of images has been analyzed in \cite{Richard??} and the same conclusion has been obtained: the calcaneus X-ray images are anisotropic. A by-product of our method is the measurement of the anisotropy through the ratio between the oriented perimeters. It will be used to produce a test of isotropy.

\bigskip

The present paper is part of the methodological literature that deals with statistical inference based on geometrical observable features. Although it is an old engineers question (see \cite{Longuet-Higgins} for instance), it has recently received much attention from a statistical point of view.  To cite some of these papers, let us quote \cite{Worsley96} where the localization of peaks are infered from the observation of the Euler chracteristic in neuroimaging, \cite{Molina} where isotropy is tested through the observation of the gradient, \cite{DEL17} or \cite{bierme2019} where a test of Gaussianity is produced based on the Euler characteristic of excursion sets, \cite{Psymetrie} where a test of symmetry is produced based on the perimeter of thresholded images,  ({\sc \`a verifier et completer avec d'autres non li\'es \`a notre "famille". Pour chacun, what is infered? and what is observed? mettre dans ordre chronologique.})\\
In particular, let us focus on two specific articles \cite{cabana1987affine, Berzin} with a similar objective as our, namely a test of isotropy, and based on similar observations, namely the length of level sets. {\sc Expliquer la methode de ces papiers et les differences avec le present papier}. Implementations of this type of method can be found in cosmology, neuroimaging and medical imaging in general, hydrology, etc.

\bigskip

%\paragraph{Outline of our method.}
Let us now present in details what is the content of our study. As already said, we aim at constructing a statistical test of isotropy based on the observation at small scale of the image. Our observation will be very sparse since it is reduced to count the horizontal and vertical edges that are involved at the interface between the black and the white pixels of the binary image. This geometrical quantity is nothing but the discrete perimeter (see \cite{HermineAgnes}), considering separately the horizontal contribution and the vertical one.

Assuming that the original grey-level image is a discrete Gaussian stationary field, we are able to explicitely compute the first two moments of the so-called "oriented perimeter". Our study of moments includes the asymptotic behavior as the number of pixels goes to infinity, as well as numerical illustrations for various Gaussian distributions. We then establish a Central Limit Theorem for the joint oriented perimeters at various levels. The perimeter being given as a sum of functionals of correlated Gaussian variables, the main argument for the CLT that we use is borrowed from Breuer-Major result as exposed in \cite{Arcones}. Let us note that a similar study was performed in \cite{Psymetrie} but under a very different context since the underlying Gaussian field was supposed to be a white noise. The totally independent structure of the pixels yield simple computations and estimations which are not allowed anymore in the correlated situation that we consider in the present paper.

The next step of our method consists in building the promised statistical test. More precisely, $\rho$ being the covariance function of the Gaussian field and $(e_1,e_2)$ being the canonical basis of $\mathbb R^2$, we consider the null hypothesis $H0:~\rho(e_1)=\rho(e_2)$ that we call "local isotropy" through a misuse of language. We exhibit a statistic depending on the ratio of both oriented perimeters that goes to zero under $H0$ thanks to the CLT previoulsy established. Moreover, we prove the consistency of the proposed test. Let us insist on the fact that our test is a non-parametric one so that the alternative hypothesis reduces to $H1:~\rho(e_1)\ne \rho(e_2)$. {\sc verifier!}

The theoretical study is completed by a large amount of numerical illustrations based on simulated data. We sample Gaussian fields with compact support covariances and use parametric deformations to get anisotropic models. The performances of our test are illustrated on those models. The crucial question of estimating the variance of the perimeter is also explored.

\bigskip

{\sc The paper is organized as follows ...}

\bigskip
\bigskip

\textcolor{blue}{

@@

By using standard ellipse, they can compute the direction of maximum variability in a direction of angle $\theta$. So, they are able to describe the spatial behavior of the mean vectors, quantifying by the calculation of $\theta$ the direction of maximum variability.

@@

Let $m$ be an integer with $m \geq 2$. Without loss of generality, we consider our observation window as the unit square $S = [0,m]^{2}$ and  we divide our window into $m^{2}$ pairwise disjoint squares. We denote by $e_1$, $e_{2}$ the elements of the canonical base of $\mathbb{R}^{2}$ and we introduce the following notations.

@@

 \item[$\bullet$] $\mathbb{G}_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \, \mathbb{Z}^{2}$ is the set of points in $S$ that are considered. We write $x = (x_1, x_2)$ with $x_1, x_2 \in \{0,\ldots, m-1\}$ for any $x\in \mathbb{G}_{m}$.
 \item[$\bullet$] For $x\in \mathbb{G}_{m}, \; C_{m}(x) \, := \,x + \text{\larger[1]{$[$}}0, 1 \text{\larger[1]{$]$}}^{2}$ will be referred to as a \textit{cell}. Note that $S~= \cup_{x \in \mathbb{G}_{m}} C_{m}(x)$.
\item[$\bullet$] We denote by  $\mathbb{E}^{(1)}_{m}, \; \mathbb{E}^{(2)}_{m} $ the set of vertical and horizontal edges in $\mathring{S}$, and for each $x \in \mathbb{G}_{m}$, we denote by $w_{i}(x)$ the intersection, $C_{m}(x) \cap C_{m}(x+e_{i})$ with $ i \in \{1, 2\}$, the edge $w_{i}(x)$  is a segment of length $1$. And finally, 

@@

$\mathbb{G}^{(1)}_{m} := \left\{ x \in \mathbb{G}_{m}; \; C_{m}(x)\cap C_{m}(x + e_{1}) \subset \mathring{S} \right\} = [\![0,m-2]\!]\times[\![0,m-1]\!], $ \\
\item $\mathbb{G}^{(2)}_{m} := \left\{ x \in \mathbb{G}_{m}; \; C_{m}(x)\cap C_{m}(x + e_{2}) \subset \mathring{S} \right\} = [\![0,m-1]\!]\times[\![0,m-2]\!]. $ \\

@@

\draw[pattern=north west lines, pattern color=green] (0,0) rectangle (1,1);
\draw[pattern=north west lines, pattern color=green] (3,1) rectangle (2,2);
\draw[red] (0.8, 0.5) -- (1.2, 0.5);
\draw[red] (0.8, 1.5) -- (1.2, 1.5);
\draw[red] (0.8, 2.5) -- (1.2, 2.5);
\draw[red] (0.8, 3.5) -- (1.2, 3.5);
\draw[red] (1.8, 0.5) -- (2.2, 0.5);
\draw[red] (1.8, 1.5) -- (2.2, 1.5);
\draw[red] (1.8, 2.5) -- (2.2, 2.5);
\draw[red] (1.8, 3.5) -- (2.2, 3.5);
\draw[red] (2.8, 0.5) -- (3.2, 0.5);
\draw[red] (2.8, 1.5) -- (3.2, 1.5);
\draw[red] (2.8, 2.5) -- (3.2, 2.5);
\draw[red] (2.8, 3.5) -- (3.2, 3.5);
\draw[step = 1cm, black, thick](8,0) grid (12,4);
\draw[pattern=north west lines, pattern color=green] (8,0) rectangle (9,1);
\draw[pattern=north west lines, pattern color=green] (11,1) rectangle (10,2);
\draw[blue] (8.5, 0.8) -- (8.5, 1.2);
\draw[blue] (9.5, 0.8) -- (9.5, 1.2);
\draw[blue] (10.5, 0.8) -- (10.5, 1.2);
\draw[blue] (11.5, 0.8) -- (11.5, 1.2);
\draw[blue] (8.5, 1.8) -- (8.5, 2.2);
\draw[blue] (9.5, 1.8) -- (9.5, 2.2);
\draw[blue] (10.5, 1.8) -- (10.5, 2.2);
\draw[blue] (11.5, 1.8) -- (11.5, 2.2);
\draw[blue] (8.5, 2.8) -- (8.5, 3.2);
\draw[blue] (9.5, 2.8) -- (9.5, 3.2);
\draw[blue] (10.5, 2.8) -- (10.5, 3.2);
\draw[blue] (11.5, 2.8) -- (11.5, 3.2);
% \foreach \y in {1,2,3,}{
%   \foreach \x in {8,9,10, 11, 12}{
%   \draw[fill = green] (\x,\y) circle (2pt);

@@

\caption{Square tiling for $m = 4$ and associated cells $C_{4}(0,0)$ and $C_{4}(2,1)$ (green stripes). We represent the vertical edges $w_{1}$ in red and  the horizontal ones $w_{2}$ in blue.}

@@

@@

% \centering
% {\includegraphics[scale=0.4]{Gaussianfiledexample.pdf}}
{\includegraphics[scale=0.25]{Gaussianrandom001.pdf}}
{\includegraphics[scale=0.25]{gaussianrandom01.pdf}}
{\includegraphics[scale=0.25]{gaussianrandom1.pdf}}
\vspace{-5cm}
% \centering
{\includegraphics[scale=0.25]{EX001.pdf}}
{\includegraphics[scale=0.25]{EX01.pdf}}
{\includegraphics[scale=0.25]{EX1.pdf}}

@@

 \caption{Generations of Gaussian random fields with covariance $\rho(x) = e^{-\kappa||x||^{2}}$ with~$m = 512$, and their respective thresholded image for $t=0$ and different values for $\kappa$, from left to right $\kappa = 0.01, 0.1, 1$, using the Matlab function \textit{stationary Gaussian process} \cite{MATLAB}.}

@@

Considering a threshold parameter $t \in \mathbb{R}$, we introduce the associated binary \linebreak image $Z^{\scriptscriptstyle (m)}_{t} = \left(\mathbbm{1}_{\left\{X_x \geq t\right\}} \right)_{x \in \mathbb{G}_{m}}$ where each cell $C_{m}(x)$ is associated to black or white according to whether~$X_{x} \geq t$ or $X_{x} < t$. 

@@

For $t\in \mathbb{R},$ we denote by $\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t)$ the sum of all contributions over the $i$th direction (vertical for $i = 1$ and horizontal for $i = 2$) and we call it the oriented perimeter of the binary image~$Z^{\scriptscriptstyle (m)}$,

@@

This result extends the one given in \cite{HermineAgnes} (Proposition 3) since we do not assume here that $\rho(e_i) > 0$. Using the former expression, we are also able to obtain an analytic expression for the first moment.
\begin{Proposition}(Analytic expression for the first moment of the oriented perimeter)
\label{analytic expression}
  \mathbb{E}\left(f^{(i)}(t) \right) = \int_{\rho(e_i)}^{1}\frac{\exp(-t^2/(1+u))}{\pi\sqrt{(1-u^2)}}du
Let $t \in \mathbb{R}$, We consider the function $h_{t}$ defined as follow \begin{align*} 
h_{t}: (-1,1) &\longrightarrow \mathbb{R}, \\
with $N \sim \mathcal{N}\left(0,1\right)$. We introduce an intermediate function $p_{t}(x) = \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right)\right)$ making use of the symmetry properties of the cumulative distribution function $\Phi$, \linebreak we have $h_{t}(x) =p_{t}(x) - 1 + p_{-t}(x)$, thus the derivative of $h_{t}$ is equal to $h_{t}'(x) = p_{t}'(x) + p_{-t}'(x)$ and 
\begin{align*}p_{t}'(x) & = \mathbb{E}\left(\frac{-2|N| -t\sqrt{2(1-x)}}{2(1+x)\sqrt{1-x^2}}\Phi'\left(\frac{2t + |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right)\right), \\
& \hspace{0.7cm}\mathbb{E}\left(\left(-2|N| -t\sqrt{2(1-x)}\right)\exp\left(\frac{-t|N|\sqrt{2(1-x)}}{1+x}\right)\exp\left(\frac{-N^{2}(1-x)}{2(1+x)}\right)\right), \\
& = \frac{\exp(-t^2/(1+x))}{4\pi(1+x)\sqrt{1-x^2}} \\
& \hspace{0.7cm} \int_{-\infty}^{\infty}\exp\left(-\frac{y^2}{1+x}\right)\left(\left(-2|y| -t\sqrt{2(1-x)}\right)\exp\left(\frac{-t|y|\sqrt{2(1-x)}}{1+x}\right)\right)dy,\\
& = \frac{\exp(-t^2/(1+x))}{2\pi(1+x)\sqrt{1-x^2}}\exp\left(\frac{t^2(1-x)}{2(1+x)}\right) \\
& \hspace{0.7cm} \int_{0}^{\infty}\left(\left(-2y -t\sqrt{2(1-x)}\right)\exp\left(-\frac{\left(y+t\sqrt{2(1-x)}/2\right)^{2}}{1+x}\right)\right)dy,  \\
\end{align*}Thus, $h_{t}'(x) = 2 \times \frac{-\exp(-t^2/(1+x))}{2\pi\sqrt{(1-x^2)}} = \frac{-\exp(-t^2/(1+x))}{\pi\sqrt{(1-x^2)}}$.
% \begin{align*}
% h'(x) & = \mathbb{E}\left( \left(\frac{2t + |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right)'\Phi'\left(\frac{2t + |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right)\right. \\
% & \hspace{5cm} \left. - \left(\frac{2t - |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right)'\Phi'\left(\frac{2t - |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right) \right)\\
% & = \mathbb{E}\left(\frac{-2|N| -t\sqrt{2(1-x)}}{2(1+x)\sqrt{1-x^2}}\Phi'\left(\frac{2t + |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right) \right. \\
% & \hspace{6cm}  \left. - \frac{2|N| - t\sqrt{2(1-x)}}{2(1+x)\sqrt{1-x^2}}\Phi'\left(\frac{2t - |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right) \right) \\
% & = \frac{1}{2(1+x)\sqrt{1-x^2}}\mathbb{E}\left(\left(-2|N| -t\sqrt{2(1-x)}\right)\Phi'\left(\frac{2t + |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right) \right. \\
% & \hspace{5.5cm}  \left. - \left(2|N| - t\sqrt{2(1-x)}\right)\Phi'\left(\frac{2t - |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right) \right) \\
% & = \frac{\exp(-t^2/(1+x))}{2\sqrt{2\pi}(1+x)\sqrt{1-x^2}}\\
% &\hspace{0.5cm} \mathbb{E}\left(\left(-2|N| -t\sqrt{2(1-x)}\right)\exp\left(\frac{-t|N|\sqrt{2(1-x)}}{1+x}\right)\exp\left(\frac{-N^{2}(1-x)}{2(1+x)}\right)\right. \\
% &\hspace{2cm}\left. - \left(2|N| - t\sqrt{2(1-x)}\right)\exp\left(\frac{t|N|\sqrt{2(1-x)}}{1+x}\right)\exp\left(\frac{-N^{2}(1-x)}{2(1+x)}\right)\right) \\
% & = \frac{\exp(-t^2/(1+x))}{4\pi(1+x)\sqrt{1-x^2}}\\
% &\hspace{0.5cm} \int_{-\infty}^{\infty}\exp\left(-\frac{y^2}{1+x}\right)\left(\left(-2|y| -t\sqrt{2(1-x)}\right)\exp\left(\frac{-t|y|\sqrt{2(1-x)}}{1+x}\right)\right. \\
% &\hspace{5cm}\left. - \left(2|y| - t\sqrt{2(1-x)}\right)\exp\left(\frac{t|y|\sqrt{2(1-x)}}{1+x}\right)\right)dy \\ 
% & = \frac{\exp(-t^2/(1+x))}{2\pi(1+x)\sqrt{1-x^2}}\exp\left(\frac{t^2(1-x)}{2(1+x)}\right)\\
% &\hspace{0.5cm} \int_{0}^{\infty}\left(\left(-2y -t\sqrt{2(1-x)}\right)\exp\left(-\frac{\left(y+t\sqrt{2(1-x)}/2\right)^{2}}{1+x}\right)\right. \\
% &\hspace{5cm}\left. - \left(2y - t\sqrt{2(1-x)}\right)\exp\left(-\frac{\left(y-t\sqrt{2(1-x)}/2\right)^{2}}{1+x}\right)\right)dy \\
% & = \frac{-\exp(-t^2/(1+x))}{2\pi(1-x)^{1/2}(1+x)^{3/2}}\exp\left(\frac{t^2(1-x)}{2(1+x)}\right)\\
% & \hspace{2cm} \left(\int_{\frac{t}{2}\sqrt{2(1-x)}}^{\infty}2z\exp\left(-\frac{z^2}{1+x}\right)dz + \int_{-\frac{t}{2}\sqrt{2(1-x)}}^{\infty}2z\exp\left(-\frac{z^2}{1+x}\right)dz \right)\\
% & = \frac{-\exp(-t^2/(1+x))(1+x)}{2\pi(1-x)^{1/2}(1+x)^{3/2}}\\
% & = \frac{-\exp(-t^2/(1+x))}{2\pi\sqrt{(1-x^2)}}.
% \end{align*}

@@

\paragraph{Total variation.}In image processing, the total variation of an image $u \in L^{1}_{loc}(\Omega)$ which is given by $\int_{\Omega}|\nabla u|dx$ is a common and well studied object. It is possible to link this quantity the perimeter of $u$, by applying the coarea formula, $\int_{\Omega}|\nabla u|dx = \int_{\mathbb{R}}\mathcal{P}(t)dt$ with $\mathcal{P}(t)$ being the perimeter associated to the level set of the image $u$ at level $t$. In the following result, by considering Proposition \eqref{propFisrtmoment}, we obtain a simple expression for the first moment of the total variation, and link it directly to the covariance evaluated in the $i$th direction.

@@

Let us now study the monotonic properties of the function $\rho \mapsto \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}(t)\right)$ where $\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}$ is the perimeter with respect of the orientation $i$ associated to the Gaussian field of covariance function $\rho$. This result allows us to state that the oriented perimeter is a strictly decreasing function with respect to $\rho$. 

@@

Let $\overline{X}, \tilde{X}$ be two stationary centered Gaussian random fields with unit variance, and $\bar{\rho}, \tilde{\rho}$ their respective covariance structure. For any level $t$, we  have the following result:

@@

@@

where $\xrightarrow[]{d}$ holds for the convergence in distribution and $\mathcal{N}\left(0,\,\Sigma_{2r}^{\textcolor{white}{}^{\star}}\right)$ for the $2r$-dimensional centered Gaussian distribution with covariance matrix $\Sigma_{2r}^{\textcolor{white}{}^{\star}}$ given by

@@

\Sigma^{\textcolor{white}{}^{\star}}_{2r}(l,i,k,j) & : = \lim_{m \to \infty}\text{Cov}\left(\frac{1}{m}\mathcal{P}^{\scriptscriptstyle (i)}_{m}(t_{l}),  \frac{1}{m}\mathcal{P}^{\scriptscriptstyle (j)}_{m}(t_{k}) \right)
